---
title: "New York Air Quality Measurements"
author: "Simone Kraemer"
date: "March 16th 2018"
output: ioslides_presentation
---

<style type="text/css">
code
{ /* Code block */
    font-size: 10px;
    line-height: 1.0;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 15px;
    line-height: 1.0;
}
</style>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(plotly)
```


## Data

The dataset used for these plots is the R dataset "airquality" which contains
daily readings of the following air quality values for May 1, 1973 (a Tuesday)
to September 30, 1973:

- Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island
- Solar.R: Solar radiation in Langleys in the frequency band 4000-7700 Angstroms from 0800 to 1200 hours at Central Park
- Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport
- Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.

In the diagrams, the ozone as a function of solar radiation, wind and temperature shall
be shown.


## Data Preparation

Load dataset and delete data where "Ozone" is NA:
```{r, echo = TRUE, comment = ""}
dataAirQuality <- airquality
dataAirQuality <- dataAirQuality[!is.na(dataAirQuality$Ozone), ]
head(dataAirQuality)
```


## 2D-diagrams: Code for data plotting

```{r, 2dplot, echo = TRUE, eval = FALSE, warning = FALSE}
# Define axis-style
x1 <- list(title = "Wind", autotick = TRUE)
x2 <- list(title = "Solar Radiation", autotick = TRUE)
x3 <- list(title = "Temperature", autotick = TRUE)
y1 <- list(title = "Ozone", showticklabels = TRUE, showline = TRUE, zeroline = TRUE)
y2 <- list(title = "", showticklabels = FALSE, showline = TRUE, zeroline = TRUE)
y3 <- list(title = "", showticklabels = FALSE, showline = TRUE, zeroline = TRUE)

# Define subplots
p1 <- plot_ly(airquality, x = ~Wind, y = ~Ozone,
              type = "scatter", mode = "markers",
              marker=list(color = "blue" , size = 10 , opacity = 0.5)) %>%
      layout(xaxis = x1, yaxis = y1, showlegend = FALSE)
p2 <- plot_ly(airquality, x = ~Solar.R, y = ~Ozone,
              type = "scatter", mode = "markers",
              marker=list(color = "orange" , size = 10 , opacity = 0.5)) %>%
      layout(xaxis = x2, yaxis = y2, showlegend = FALSE)
p3 <- plot_ly(airquality, x = ~Temp, y = ~Ozone,
              type = "scatter", mode = "markers",
              marker=list(color = "red" , size = 10 , opacity = 0.5)) %>%
      layout(xaxis = x3, yaxis = y3, showlegend = FALSE)

# Put subplots together to one plot
p2d <- subplot(p1, p2, p3, titleX = TRUE, titleY = TRUE)
hide_legend(p2d)
p2d
```


## 2D-diagrams:

```{r, 2dplot, echo = FALSE, eval = TRUE, warning = FALSE}
```


## 3D-diagram: Code for data plotting

```{r, 3dplot, echo = TRUE, eval = FALSE, warning = FALSE}

# Define axis-style
x <- list(title = "Wind", autotick = TRUE)
y <- list(title = "Temperature", showticklabels = TRUE, showline = TRUE,
          zeroline = TRUE)
z <- list(title = "Solar Radiation", showticklabels = FALSE, showline = TRUE,
          zeroline = TRUE)
title <- "Ozone"

# Define plot
p3d <- plot_ly(airquality, x = ~Wind, y = ~Temp, z = ~Solar.R,
               type = "scatter3d", mode = "markers", color = ~Ozone,
               colors = "Blues",
               marker = list(size = 10 , opacity = 1.5)) %>%
       layout(title = title,
              scene = list(xaxis = x, yaxis = y,zaxis = z))
p3d
```


## 3D-diagram:

```{r, 3dplot, echo = FALSE, eval = TRUE, warning = FALSE}
```


## Result

It can be seen that there is a clear trend between  

- Wind and Ozone: The higher the wind speed is, the lower the ozone values are
- Temperature and Ozone: The higher the temperature is, the higher the ozone 
values are

For solar radiation and ozone the trend is not that clear, although a slight increase
of ozone for higher solar radiation can be seen.
